---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : ""
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : ""
    affiliation   : ""

affiliation:
  - id            : ""
    institution   : ""

bibliography      : 
  - "../references.bib" 
          
floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE, warning = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models', include = FALSE}
source(here::here("scripts", "02_load_data.R"))
source(here::here("scripts", "01_helpers.R"))

# Get path to saved models
gca_mods_path  <- here("mods", "stress", "gca")

# Load models as list and store full mod to global env
load(paste0(gca_mods_path, "/gca_mon_mods_sum.Rdata"))
load(paste0(gca_mods_path, "/gca_l2_mods_sum.Rdata"))
load(paste0(gca_mods_path, "/model_preds_sum.Rdata"))
load(paste0(gca_mods_path, "/model_preds_l2_sum.Rdata"))
load(paste0(gca_mods_path, "/nested_model_comparisons_l2_sum.Rdata")) #includes mon

```




```{r, 'plot-time-course', echo=FALSE, fig.cap="Figure 3. Gaze fixation patterns on target from 500 ms before target syllable offset to 1000 ms after as a function of L1 and stress condition."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_l1.png")
)
```


```{r, 'write-up-prep-mon', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations

params <- gca_mod_mon_final %>% #gca_mon_mods_sum$
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:3, 0)) 

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0)) 

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# # Pre-calculate intercept as proportion
# b0 <- params$B[params$subscript == "00"] %>% as.numeric
# b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

```


```{r, table-mon-params, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_mon_mods$gca_mod_mon_final %>%  
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:2, 0))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 


```

We conducted a GCA on SS and took them as reference when discussing our findings.
Figure 4 shows the GCA model fit for SS.
The GCA intercept for SS was positive and significant, indicating this group was anticipating at suffix onset.
The probability of SS fixating on the target was 0.953 (LB = 0.942; UB = 0.962) averaging across stress conditions, which indicates they were fixating on the target verb above chance at suffix onset.
There were main effects on the linear (`r report_row('2')`) and quadratic (`r report_row('3')`) polynomial time terms.
Since they improved the model, we kept them.


```{r, table-mon-probs, eval=T, echo=F, include = F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)


target_offset_preds_mon %>% #model_preds$
  mutate(stress = if_else(stress == 1, "Present", "Preterit")) %>% 
  arrange(stress) %>% 
  group_by(stress) %>%
  distinct() %>%
  #ungroup() %>%
  mutate(
         stress = blank_same_as_last(as.character(stress))) %>%
  select(`Lexical stress` = stress, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)

```


```{r, 'plot-preds-mon', echo=FALSE, fig.cap="Figure 4. Growth curve analysis estimates of fixations on target as a function of lexical stress for the Spanish monolingual speakers during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_mon.png")
)
```




```{r, 'write-up-prep-dele', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_mod_l2_final %>% #gca_l2_mods_sum$
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:3, 0))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

```

```{r, table-dele-params, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_l2_mod_dele_final %>%  #gca_l2_mods_sum$
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:2, 2))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 


```

Table 2: Growth curve model fixed effects for L2 speakers (proficiency).


```{r, table-dele-probs, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)


target_offset_preds_dele %>% #model_preds_sum$
  mutate(stress = if_else(stress == 1, "Present", "Preterit"),
         l1 = if_else(l1 == -1, "English", "Mandarin"),
         l1 = fct_relevel(l1, "English", "Mandarin")) %>% 
  arrange(l1, stress) %>% 
  group_by(l1, stress) %>%
  distinct() %>%
  #ungroup() %>%
  mutate(l1 = blank_same_as_last(as.character(l1)),
         stress = blank_same_as_last(as.character(stress))) %>%
  select(L1 = l1, `Lexical stress` = stress, Proficiency = DELE, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)

```

*Table 3*: Model estimates for probability of target fixations ±SE at 200 ms after the target syllable offset as a function of L2 proficiency. (LB = lower bound; UP = upper bound).


The linear (`r report_row(2)`) and cubic (`r report_row(4)`) polynomial time terms estimates reached significance, and thus we kept them in the model.
There was a main effect of L1 (`r report_row(5)`), which indicates that there was a difference in the log odds of Mandarin speakers fixating on the target, such that they were fixating less on the target at suffix onset.
There was a main effect of proficiency as well (`r report_row(7)`), pointing towards an association between increased fixations for each extra score in proficiency.


```{r, 'plot-preds-dele', echo=FALSE, fig.cap="Figure 5. Growth curve analysis estimates of fixations on target as a function of lexical stress for each L2 group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "prof_sum.png")
)
```






```{r, 'write-up-prep-use', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_l2_mod_use_final %>% # gca_l2_mods_sum$
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1),
    paste0(0:4, 2))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:4, 2))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

```


```{r, table-use-params, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_l2_mod_use_final %>%  #gca_l2_mods_sum$
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:2, 2))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

*Table 4*: Growth curve model fixed effects for L2 speakers (L2 use).

The GCA analysis with L2 weekly use in percentage estimates the intercept log odds at `r report_row(1)` for the L2 speakers. 
The estimated probabilities of target fixations (Table 5) on the target at suffix onset in this model indicate all L2 speakers were fixating on the target above chance, which we take to mean they were anticipating the suffix they were going to hear.
The two values in the column Weekly L2 % use represent the minimum and the maximum L2 use reported by the participants.
Taking into account Spanish use for the probabilities, Table 5 shows that the more frequent the weekly L2 use, the greater the probability of prediction is in the present tense, but surprisingly, not in the preterit tense. 


```{r, table-use-probs, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

use_prob <- target_offset_preds_use %>% #model_preds$
  mutate(stress = if_else(stress == 1, "Present", "Preterit"),
         l1 = if_else(l1 == -1, "English", "Mandarin Chinese"),
         l1 = fct_relevel(l1, "English", "Mandarin Chinese")) %>% 
  group_by(l1, stress) %>%
  # filter(., percent_l2_week == max(percent_l2_week) | 
  #          percent_l2_week == min(percent_l2_week)) %>%
  distinct() %>%
  # ungroup() %>%
  arrange(l1, stress) %>% 
  mutate(l1 = blank_same_as_last(as.character(l1)),
         stress = blank_same_as_last(as.character(stress))) %>%
  select(L1 = l1, `Lexical stress` = stress, `L2 use` = use, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)

save_as_docx(dele_probs, dele_params, use_prob, use_params, path = here::here('prob.docx'))
# save_as_docx(dele_prob, use_prob, path = here::here('prob.docx'))
```

*Table 5*: Model estimates for probability of target fixations ±SE at 200 ms 
after the target syllable offset as a function of L2 weekly % use. (LB = lower bound; UP = upper bound).


The estimates of the linear (`r report_row(2)`) and cubic (`r report_row(4)`) polynomial time terms were significant.
These effects suggest differences in slope and bow curve across conditions. 
Since they improved the model, we kept them.

There was an effect of L1 as in the proficiency model (`r report_row(5)`), which we interpret again as a sign that English speakers were fixating on the target more than Mandarin speakers at suffix onset.
This effect appeared also in the linear term (`r report_row(8)`).
This effect indicates the slope for Mandarin speakers was less steep, as observed in Figure 6a.
The steeper slope for English speakers in comparison to Mandarin speakers suggests English speakers were increasing fixations on the target faster.
There is also an effect of L2 use in the linear term (`r report_row(11)`).
Following the same reasoning as for L1, a larger value in the estimate is associated with a steeper rise, associated with faster increase of fixations as proficiency improves.


```{r, 'plot-preds-use-l1', echo=FALSE, fig.cap="Figure 6a. Growth curve analysis estimates of fixations on target as a function of lexical stress and L2 weekly use for each L2 group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "use_sum.png")
)
```


There was an effect of lexical stress in the quadratic term (`r report_row(10)`).
This effect indicates the curve was more bowed in preterit than in present tense.
The closer curve in preterit indicates that tense elicited fixations on the target earlier than present tense, as Figure 6b shows.


```{r, 'plot-preds-use-cond', echo=FALSE, fig.cap="Figure 6b. Growth curve analysis estimates of fixations on target as a function of lexical stress and L2 weekly use for each L2 group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "use_sum_cond.png")
)
```














# Other plots






# Tables 

## Model estimates at target syllable offset  

```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

mon_preds %>% 
  mutate(cond = if_else(stress == 1, "Present", "Preterit")) %>% 
  # arrange(cond, ospan) %>% 
  arrange(cond) %>%
  group_by(cond) %>%
  mutate(prob = mean(prob),
         prob_lb = mean(prob_lb),
         prob_ub = mean(prob_ub)) %>%
  mutate(cond = blank_same_as_last(as.character(cond))) %>%
  # group_by(cond) %>%
  # filter(., ospan == max(ospan) |
  #          ospan == min(ospan)) %>%
  # ungroup() %>%
  select(`Lexical stress` = cond, Probability = prob, #ospan, 
         LB = prob_lb, UB = prob_ub) %>%
  distinct() %>%
  flextable() %>% 
  #width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```
*Table 1*: Model estimates for probability of target fixations in monolinguals ±SE at 200 ms 
after the target syllable offset. (LB = lower bound; UP = upper bound).

## Fixed effects

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_mon_mods$gca_mod_mon_base %>% 
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

# pretty_fixed_effects <- pretty_fixed_effects[0:4,]

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 2. Growth Curve Analysis fixed effects (monolinguals)








```{r, warning=F}

# # Get full mod and make it pretty for the table
# pretty_fixed_effects <- gca_l2_mod_wm_final %>%  #gca_l2_mods$
#   tidy_lme4() %>% 
#   mutate(p = format_pval(p), 
#          Parameter = fix_param_names(Parameter)) %>% 
#   mutate_each(funs(format_fixef_num), Estimate:t) %>% 
#   rename(`_t_` = t, `_p_` = p) 
# 
# # Include gammas (Gij) after each parameter name
# subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
#           paste0(0:3, 2))
# var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
# pretty_fixed_effects$Parameter %<>% paste(., var_labels)
# 
# pretty_fixed_effects %>% 
#   knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 0: Growth curve model fixed effects L2 (WM)


## Random effects

```{r, 'ranef-table-mon', results = "asis"}
ranef_table <- gca_mon_mods$gca_mod_mon_final %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```




Appendix 5.Growth curve model random effects (monolinguals)





```{r, 'ranef-table-l2', results = "asis"}
ranef_table <- gca_l2_mods$gca_l2_mod_use_final %>% # Ranef same for DELE and USE
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```

Appendix 6: Growth curve model random effects (L2)

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refere"></div>
\endgroup
